### 2020-07-27 draft.Rmd
fix inline R calc
Add transformation language, describe the RCT, and add sample size information

@@

@@

The data and code for [@Ashraf2006] are available on the Harvard Dataverse [@Data]. The repository contains Stata `.do` files for all models and tables included in the authors' paper. The repository contains three data sets.

The first contains information after six months. The second contains information after twelve months. The third data set contains information about the change in balances after six months and twelve months. The authors did not include documentation for the numerous variables included in the data set. We recreated Table II, Table VI, and Table VII in `R` to back out the variable definitions and confirm that the published table matches the published table.

todo(aaron): include a brief visual summary of the data

Number of observations

@@

log; however, non-positive values

@@

The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months. Accordingly, the dependent variable is not approximately normally distributed and the error term of their estimated models is not approximately normally distributed.

The SEED treatment, the marketing control, and the full control all have outliers. Though the SEED treatment's outliers are distinct for the change in twelve month balance.

# measure of outliers from 611?

[@Ashraf2006] found only modest evidence for a statistically significant intent-to-treat (ITT) effect for the commitment savings accounts using ordinary least squares regression (OLS). Furthermore, they found that the differential effect of being offered the commitment savings product beyond being offered only a marketing treatment was indistinguishable from zero.

@@

```{r results = "asis"}
#
# OLS model
#
six_months = filter(seed011204, !is.na(treatment))

@@

>>>>

The authors partnered with a rural bank in Mindanao, Philippines called Green Bank of Caraga. After two rounds of randomization, they ended up with a survey size of 1,777 people who completed a baseline household survey. They then randomly assigned the individuals to the commitment treatment (T), marketing-treatment (M), and control (C) groups. One concern is that the commitment-savings may have a treatment effect because of the outreach or positive messaging around savings. The marketing treatment (M), a special visit to encourage savings using existing savings products only, was included to evaluate this effect. The marketing-treatment can also be thought of as a control. There were no pre-treatment significant differences between the three groups for observable characteristics.

The two main outcomes of interest are 1. take-up of the commitment savings product and 2. savings at the financial institution. The authors use the baseline household survey to evaluate if there are any predictors to take-up. Savings balances at the institution, and not just in the commitment savings account, partially accounts for crowd-out to other savings vehicles.

@@

todo(aaron): address quantile regression

@@

The data and code for [@Ashraf2006] are available on the Harvard Dataverse [@Data]. The repository contains Stata `.do` files for all models and tables included in the authors' paper.

The repository contains three data sets. All three data sets include identifiers and certain demographic information. The first data set contains outcome information after six months. The second data set contains outcome information after twelve months. The third data set contains information about the change in balances after six months and twelve months. The authors did not include documentation for the numerous variables included in the data set. We recreated Table II, Table VI, and Table VII in `R` to back out the variable definitions and confirm that the published table matches the published table.

The authors began with a sample of 4,001 clients who have savings accounts in of two bank branches in the greater Butuan City area and have identifiable addresses. A second randomization resulted in 3,154 potential surveys and 1,777 completed surveys.

@@

@@

The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months as demonstrated in [todo(aaron): add plot number from above]. Accordingly, the dependent variable is not approximately normally distributed and the error term of their estimated models is not approximately normally distributed.

[todo(aaron): add plot number from above] The SEED treatment, the marketing control, and the full control all have outliers. Though the SEED treatment's outliers are distinct for the change in twelve month balance.

A normal distribution and ordinary least squares regression do not seem appropriate in this situation. One option is to transform the outcome variable before estimation so that normal-theory methods can be applied to the data. A log transformation would be appropriate but the presence of non-positive numbers would lead to an undefined outcome. An inverse hyperbolic sine transformation [@Burbidge] or Yeo-Johnson transformation [@Yeo] could result in a similar transformation to a log transformation and be robust to non-positive numbers.

[@Ashraf2006] estimate their models on the untransformed data and find only modest evidence for a statistically significant intent-to-treat (ITT) effect for the commitment savings accounts using ordinary least squares regression (OLS). Furthermore, they found that the differential effect of being offered the commitment savings product beyond being offered only a marketing treatment was indistinguishable from zero.

@@

```{r results = "asis"}
#
# OLS model
#

@@

1. plot residuals
2. measures of outliers
